---
title: "Bioconductor Project"
author: Hannah Hellmuth and Lindsey Ukishima
format: html
editor: visual
---

# Workflow: generegulation

Citation: Bioconductor Package Maintainer (2022). *generegulation: Finding Candidate Binding Sites for Known Transcription Factors via Sequence Matching*. R package version 1.23.0, <https://www.bioconductor.org/help/workflows/generegulation/>.

#### Finding Candidate Binding Sites for Known Transcription Factors via Sequence Matching

The binding of transcription factor proteins (TFs) to DNA promoter regions upstream of gene transcription start sites (TSSs) is one of the most important mechanisms by which gene expression, and thus many cellular processes, are controlled. Though in recent years many new kinds of data have become available for identifying transcription factor binding sites (TFBSs) \-- ChIP-seq and DNase I hypersensitivity regions among them \-- sequence matching continues to play an important role. In this workflow we demonstrate Bioconductor techniques for finding candidate TF binding sites in DNA sequence using the model organism Saccharomyces cerevisiae. The methods demonstrated here apply equally well to other organisms.

### Installing the Package

(For R version 4.2)

```{r}
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("generegulation")
library(generegulation)
```

### Documentation

```{r}

browseVignettes("generegulation")
```

### Data

### Methods

### Results

### Conclusion
